Initial Analysis

### 2019-11-11 Initial_Analysis.Rmd
Fixed details on species status function related to the saving part

# Spp <- 601417

EstSppStatus <- function(Spp,Coord,Save_Path = "NA", Per_Taxa = F){

@@

    Save_path <- NA

    if(is.na(Save_path) == TRUE){

@@

    # File name for each species
    Name <- paste(Save_Path,"Stock_Status/",Spp,"_Status.csv",sep="")

    # Save file for each species
    write_csv(Status_Data,
              Data_Name)
  }else{

@@

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List,
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

>>>>

Spp <- 601417
Coord = CoorG
EstSppStatus <- function(Spp,Coord, Save_Path = "NA", Per_Taxa = NA){

@@

   # Select onlyZ 
    Status_Data <- Status_Data %>%
      ungroup() %>%
      select(TaxonKey,Territory,Year, Status)

    if(is.na(Save_Path) == TRUE){

@@

    # File name for each species
    Name <- paste(Save_Path,Spp,"_Status.csv",sep="")

    # Save file for each species
    write_csv(Status_Data,
              Name)
  }else{

@@

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
   Species_List[1:2],
      FUN = EstSppStatus,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
   Per_Taxa = T,
   Save_Path = "Z:/Vicky/Stock_Status/"
   )
  )
